\documentclass{article}
\usepackage[switch, modulo]{lineno}
\linenumbers
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{setspace}
\usepackage{standalone}
%removes default indents and sets paragraph spaces to custom size
\usepackage{parskip}
\parindent0pt
\parskip5pt


\usepackage{float}
\usepackage{amsfonts,amsmath,amsthm,amssymb,wasysym,latexsym,mathtools}
\usepackage{verbatim,graphicx,rotating}
\usepackage{enumerate,multirow,caption,subcaption,tabu,array,tabularx,longtable}
\usepackage{tikz,tkz-graph}
%\usetikzlibrary{calc}
\usepackage{caption}
%\usepackage{tikz-network}
%\usepackage[demo]{graphicx}
\usepackage[makeroom]{cancel}
\usepackage{colortbl,color,xcolor}
\usetikzlibrary{shapes}
\tikzstyle{vertex}=[circle, draw, inner sep=1pt, fill, minimum size=4pt]
\newcommand{\vertex}{\node[vertex]}

\newenvironment{case}[1][]{\refstepcounter{case}\par\medskip
   \textbf{Case~\thecase. #1} \rmfamily}{\newline}
\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}[section]
  \theoremstyle{definition}
  \newtheorem{definition}[thm]{Definition}
  \theoremstyle{plain}
  \newtheorem{problem}[thm]{Problem}
  \theoremstyle{plain}
  \newtheorem{conjecture}[thm]{Conjecture}
  \theoremstyle{plain}
  \newtheorem{lemma}[thm]{Lemma}
  \newtheorem{observation}[thm]{Observation}
  \newtheorem{corollary}[thm]{Corollary}
  \newtheorem{construction}[thm]{Construction}
  \newtheorem{algorithm}[thm]{Algorithm}
 %% \newtheorem{case}{\normalfont Case}
  \newtheorem{example}[thm]{Example}
\newcounter{case}[thm]

  \providecommand{\conjecturename}{Conjecture}
  \providecommand{\lemmaname}{Lemma}
  \providecommand{\problemname}{Problem}
\providecommand{\theoremname}{Theorem}
\newcommand{\noun}[1]{\textsc{#1}}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\DeclareMathOperator{\lcm}{lcm}
\DeclareMathOperator{\indeg}{indeg}
\DeclareMathOperator{\outdeg}{outdeg}
\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}

\newcommand{\GG}{\ensuremath{\mathcal{G}}}
\newcommand{\BB}{\ensuremath{\mathcal{B}}}
\newcommand{\ZZ}{\ensuremath{\mathbb{Z}}}
\newcommand{\NN}{\ensuremath{\mathbb{N}}}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{Designs for forests with seven edges} }
\author{Daniel Banegas and Bryan Freyberg$\footnote{\texttt{email: frey0031@d.umn.edu}}$ \\
Department of Mathematics and Statistics,\\ University of Minnesota Duluth,
 \\1117 University Drive, Duluth, MN 55812
 }
  
\date{} \maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Read our paper!
 \end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}\label{sec:Introduction}

 \input{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Tools}\label{sec:Tools}
 
 \input{Tools}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
 \section{Main Results}\label{sec:Main Results}
 
 \input{Main Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
 \begin{thebibliography}{10}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \bibitem{AFFK}
 J. Ahern, B. Freyberg, D. Froncek, M. Keranen, Decompositions of complete graphs into disconnected unicyclic graphs with six edges, \emph{Preprint}.
 
 \bibitem{bermond3}
 J.C. Bermond, 
 \emph{Cycles dans les graphes et $G$-configurations,}
 PhD Thesis, University of Paris XI,
 Orsay, 1975.
 
 \bibitem{bermond1}
 J.C. Bermond, C. Huang., A. Rosa, and D. Sotteau, 
 Decomposition of complete graphs into isomorphic subgraphs with five vertices, 
 \emph{Ars Combin.} 
 \textbf{10} (1980), 211--254.
 
 \bibitem{bermond2}
 J.C. Bermond and J. Sch\"onheim, 
 $G$-decomposition of $K_n$, where $G$ has four vertices or less,
 \emph{Discrete Math.} 
 \textbf{19} (1977), 113--120.
 
 \bibitem{cain}
 P. Cain, 
 Decomposition of complete graphs into stars, 
 \emph{Bull. Austral. Math. Soc.} 
 \textbf{10} (1974), 23--30.
 
 \bibitem{dewerra}
 D. de Werra, 
 On some combinatorial problems arising in scheduling, 
 \emph{Can. Operational Res. Soc. J.}
 \textbf{8} (1970), 165--175.
 
 \bibitem{Saad} 
 S. El-Zanati and C. Vanden Eynden, 
 On Rosa-type labelings and cyclic
 graph decompositions, 
 \emph{Math. Slovaca} \textbf{59(1)} (2009), 1--18.
 
 \bibitem{FreyTran}
 B.~Freyberg and N.~Tran,
 {Decomposition of complete graphs into bipartite unicyclic graphs with eight edges},
 \emph{J. Combin. Math. Combin. Comput.},  \textbf{114} (2020), 133--142.
 
 \bibitem{froncek}
 D.~Fron{c}ek and B.~Kubesa,
 {Decomposition of complete graphs  into connected  unicyclic bipartite graphs with seven edges},
 \emph{Bull. Inst. Combin. Appl.},  \textbf{93} (2021), 52--80.
 
 \bibitem{FroncekUROP}{D. Froncek and A. Sailstad}{Decompositions of complete graphs into forests with five edges}{2024}
 
 \bibitem{hanani}
 H. Hanani, 
 The existence and construction of balanced incomplete block designs, 
 \emph{Ann. Math. Statist.} \textbf{32} (1961), 361--386.
 
 \bibitem{huang}
 C.~Huang and A.~Rosa, 
 {Decomposition of complete graphs into trees},
 \emph{Ars Combin.} \textbf{5} (1978), 23--63.
 
 \bibitem{kang} 
 Q. Kang and Z. Wang, 
 Optimal packings and coverings of $\lambda K_{v}$ with graphs $K_{5}-P_{5}$, 
 {\em Bull. Inst. Combin. Appl.}
 \textbf{41} (2004),  22--41.
 
 \bibitem{kirkman}
 T.P. Kirkman,
 On a problem in combinations,
 \emph{Cambridge and Dublin Math. J.}
 \textbf{2} (1847), 191--204.
 
 \bibitem{kotzig}
 A. Kotzig, 
 Decomposition of a complete graph into $4k$-gons, 
 \emph{Mat.-Fyz. \v Casopis Sloven. Akad. Vied} 
 \textbf{15} (1965), 229--233.
 
 \bibitem{MM}
 M. Miszka. Personal Communication (2024).
 
 \bibitem{rosa} 
 A. Rosa, 
 {\em On certain valuations of the vertices of a graph}, 
 {In: Theory of Graphs (Intl. Symp. Rome 1966)}, Gordon and Breach, Dunod, Paris, 1967, 349--355.
 
 \bibitem{yamamoto}
 S. Yamamoto, H. Ikeda, S. Shige-eda, K. Ushio, and N. Hamada,
 On claw-decomposition of complete graphs and complete bigraphs,
 \emph{Hiroshima Math.}
 \textbf{5} (1975), 33--42.
 
 \bibitem{yin} J. Yin and B. Gong, Existence of $G$-designs with $|V(G)|=6$, In: W.D. Wallis et al (eds), Combinatorial designs and applications, Marcel Dekker, New York, 1990, 201--218.
 
 \end{thebibliography}
 %%%%%%%%%
\end{document}